DM: A Distributed Decision Making Model for \\ Dynamic Formation of Web services Communities

### 2014-12-06 papers/webservice-coalition-learning/webservice_coalition_learning.tex
changes

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
%\title{A Distributed Mechanism for Intelligent \\ Web Service Community Formation}
\title{TDM: Training data-based Model for \\ Dynamic Formation of Web services Communities}
%
%
%
% author names and IEEE memberships
% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
% a structure at a ~ so this keeps an author's name from being broken across
% two lines.
% use \thanks{} to gain access to the first footnote area
% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
% was not built to handle multiple paragraphs
%
%
%\IEEEcompsocitemizethanks is a special \thanks that produces the bulleted
% lists the Computer Society journals use for "first footnote" author
% affiliations. Use \IEEEcompsocthanksitem which works much like \item
% for each affiliation group. When not in compsoc mode,
% \IEEEcompsocitemizethanks becomes like \thanks and
% \IEEEcompsocthanksitem becomes a line break with idention. This
% facilitates dual compilation, although admittedly the differences in the
% desired content of \author between the different types of papers makes a
% one-size-fits-all approach a daunting prospect. For instance, compsoc
% journal papers have the author affiliations above the "Manuscript
% received ..."  text while in non-compsoc journals this is reversed. Sigh.

@@

In this paper, we introduce DLISA (Distributed Learning-based Intelligent Service Agents) community framework that operates based on a trained model that regulates web service agents' decision making process in terms of cooperating with one another. This model uses the trained data in the form of information obtained from a large number of web services regarding their single and cooperative utilities as well as environmental parameters such as demand, service quality, etc. 
%The training model deploys a logistic regression algorithm to build a hypothesis function that can thoroughly address the aforementioned research problems. 
The training model utilizes web services with enough information to efficiently decide and predict the outcome of their moves amongst the available services accessible to them. This model works in distributed manner in which our services are self-sufficient in decision making process and do not rely on a centralized decision maker process. Our findings show that communities of web services can efficiently find the appropriate web service to invite cooperating with them as well as allowing a single web service to find the best communities to join them. Furthermore, after being trained, web services get to compute expectations as utilities they would gain while cooperating with communities of different characteristics. In contrast, communities can consider the training and analyze the characteristics of different individual web services and make prudent decisions when inviting a web service to join or accepting a join inquiry initiated from a web service. In general, DLISA equips web services with efficient methods for foreseeing how their choices will impact their long-term and short-term goals; therefore, opting for best decision available.

@@

\section{Preliminaries and Problem Statement}\label{s:preliminaries}
In this section, we first present the architecture of DLISA. We explore the characterestics of intelligent service agents and the features we extract for training. To do this, we first discuss some preliminaries.

@@

In this section, we describe our training process and the methodology used to equip web services with a decision making mechanism. In this methodology, we first present the training process and then we evaluate the learning model for web services in community settings.

>>>>

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
%\title{A Distributed Mechanism for Intelligent \\ Web Service Community Formation}
\title{DM: A Distributed Decision Making Model for \\ Dynamic Formation of Web services Communities}
%
%
%
% author names and IEEE memberships
% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
% a structure at a ~ so this keeps an author's name from being broken across
% two lines.
% use \thanks{} to gain access to the first footnote area
% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
% was not built to handle multiple paragraphs
%
%
%\IEEEcompsocitemizethanks is a special \thanks that produces the bulleted
% lists the Computer Society journals use for "first footnote" author
% affiliations. Use \IEEEcompsocthanksitem which works much like \item
% for each affiliation group. When not in compsoc mode,
% \IEEEcompsocitemizethanks becomes like \thanks and
% \IEEEcompsocthanksitem becomes a line break with idention. This
% facilitates dual compilation, although admittedly the differences in the
% desired content of \author between the different types of papers makes a
% one-size-fits-all approach a daunting prospect. For instance, compsoc
% journal papers have the author affiliations above the "Manuscript
% received ..."  text while in non-compsoc journals this is reversed. Sigh.

@@

In this paper, we introduce DLISA (Distributed Learning-based Intelligent Service Agents) community framework that operates based on a decision model that regulates web service agents' decision making process in terms of cooperating with one another. The decision model in extracted from a data model in the form of information obtained from a large number of web services regarding their single and cooperative utilities as well as environmental parameters such as demand, service quality, etc. 
%The training model deploys a logistic regression algorithm to build a hypothesis function that can thoroughly address the aforementioned research problems. 
The decision model utilizes web services with enough information to efficiently decide and predict the outcome of their moves amongst the available services accessible to them. This model works in distributed manner in which our services are self-sufficient in decision making process and do not rely on a centralized decision maker process. Our findings show that communities of web services can efficiently find the appropriate web service to invite cooperating with them as well as allowing a single web service to find the best communities to join them. Furthermore, the decision model provides web services with expectations of utilities they would gain while cooperating with communities of different characteristics. In contrast, communities can consider the decision model and analyze the characteristics of different individual web services and make prudent decisions when inviting a web service to join or accepting a join inquiry initiated from a web service. In general, DLISA equips web services with efficient methods for foreseeing how their choices will impact their long-term and short-term goals; therefore, opting for best decision available.

@@

\section{Preliminaries and Problem Statement}\label{s:preliminaries}
In this section, we first present the architecture of DLISA. We explore the characteristics of intelligent service agents and the features we extract for training. To do this, we first discuss some preliminaries.

@@

In this section, we describe our data extraction process and the methodology used to equip web services with a decision making mechanism. In this methodology, we first present the data extraction and engineering process and then we evaluate the decision making mechanism for web services in community settings.
